\section{Task Allocation and Overall Plan}
We have divided our project into the following 5 tasks:
\begin{enumerate}
\item \textit{Environmental Setup}: Setup the Xilinx Zedboard and make choice
evaluate the pros and cons of using a bare-metal OS against using Linux.
\item \textit{Deployment of OS}: Depending on the choice we make in step 1, we
would either have to port the bare-metal OS for multicore systems or strip down
Linux to a simpler OS.
\item \textit{Communication Interface}: Design and implement the communication
interface. 
\item \textit{Implementation of LST}: Implement the LST scheduling algorithm on 
programmable FPGA. 
\item \textit{Evaluation}: Performance analysis of LST.
\end{enumerate}
We have a strong team to bring this project to fruition. We have divided
the tasks among ourselves in a manner which would allow us to make progress in
our respective tasks in parallel. Renato Mancuso, with his strong background in
real time operating systems would carry out tasks 1 and 2. While, during the
same phase,
Prakalp Srivastava would work on task 3, an efficient FPGA implementation of LST. Once
completed, we would work together on the design and implementation of
communication interface between the OS and the scheduler and subsequently
proceed to evaluation of our design.

In the interest of time, we have limited the goals of this project to performance
evaluation of LST. However, we also plan to pursue this work beyond the course
timeline and evaluate
the power benefits of hardware LST over Pfair and software implementations of
LST. 

